---
author: Julian Dehne
title: Expert in Learning Technologies and CSS
format:
  classic-cv-pdf: default
cvfooter:
  left: "Julian Dehne"
  right: "https://juliandehne.github.io"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Research Software Engineer, GESIS
    right: Cologne, Germany
  - title: Field
    left: Software Engineering, Social Sciences, Education
    right: https://juliandehne.github.io
  - title: Techs
    left: Python, Scala, Java, R, Transformers
    right: julian.dehne@gmail.com
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary


After completing a BA in European Studies at the University of Passau, I sought to enhance my background with expertise in Computer Science. The dual subject teacher program in Brandenburg and Berlin uniquely offered a combination of Political Science and Computer Science, which aligned perfectly with my interests. In Potsdam, I later received my PhD in the field of learning technologies.

Following my PhD, I briefly joined Humboldt University in Berlin, where I co-authored one of the first conceptual papers on fostering creativity through e-learning. Subsequently, I decided to return to the social sciences, accepting a PostDoc position at the University of Göttingen in the CSS field. Here, our team has been developing an innovative chatbot designed to facilitate deliberation on social media, which is nearing operational functionality.


# Experience


```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Research Software Engineer", "GESIS - Leibniz Institute for the Social Sciences", "May 2024 - Present",
    "Transparent Social Analytics, Department of Computational Social Science", c("Development Lead of a project to build an Open Science platform with reusable code and tutorials", "Research on Data Quality Standards", "Implementation of tools to enhance reproducibility and facilitate research with automated quality data checks"),
    "Post Doctoral Researcher", "University of Göttingen", "Aug. 2021 - May 2024",
    "Department of Methods in Social Sciences", c("Research on Deliberation on Social Media", "Constructing Human-In-The-Loop Experiments with Reddit and Twitter, NLP with Python"),
    "Post Doctoral Researcher", "Humboldt University Berlin", "Apr. 2020 - Feb. 2021", "Chair of Learning Technologies", c("Developing new methods to detect creativity in texts", "Machine Learning", "Gathering and analyzing large datsets from E-learning Platforms"),
    "Ph.D. Candidate", "University of Potsdam", "Oct. 2012 - Oct. 2020", "Chair of Complex Computational Media Applications", c("Developing new methods to support Group Formation", "Developing Sementic Database of Learning Goals", "Developing a Framework for Inquiry Based Learning", "Developing a methodology for the Evaluation of E-Learning")
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Ph.D. in Computer Science", "University of Potsdam", "Potsdam, Germany", "Nov. 2012 - Sep. 2020", c("Thesis: Possibilities and Limitations of Media Support for Inquiry-Based Learning", "Explores the use of computer technology to support inquiry-based learning in higher education"),
    "BA and MA in Computer Science, Political Science and Education", "University of Potsdam", "Potsdam, Germany", "Sep. 2009 - Okt. 2014", c("Thesis: An Intelligent Competence Database", "Implementation and Evaluation of a Learning Outcome Storage connected to Portfolio Learning"),
    "BA in European Studies", "University of Passau", "Passau, Germany", "April. 2007 - Okt. 2009", c("Thesis: Innenpolitische Bedingtheit europäischer Migrationspolitik", "Studying the Multilevel European System and how the Regions influenced the Amsterdam Treaty")
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```
