---
author: Julian Dehne
title: Learning Technologies and Computational Social Sciences
format:
  classic-cv-pdf: default
cvfooter:
  left: "Julian Dehne"
  right: "https://juliandehne.github.io"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Status
    left: Research Software Engineer, GESIS
    right: Cologne, Germany
  - title: Field
    left: Software Engineering, Social Sciences, Education
    right: https://juliandehne.github.io
  - title: Techs
    left: Python, Scala, Java, R, Transformers
    right: julian.dehne@gmail.com
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}",
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")

    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary


I am a group lead for Research Software Engineering (RSE) at the German Computer Society, with a strong background in developing open science platforms, research software, and tools to enhance reproducibility and data quality in social sciences. My current role involves leading a project to develop a RSE master program and accompanying research.

Previously, I worked as a Postdoctoral Researcher at the University of Göttingen, focusing on social media deliberation, conducting human-in-the-loop experiments with platforms like Reddit and Twitter, and applying NLP techniques in Python. At Humboldt University Berlin, I researched text-based creativity detection using machine learning and analyzed large datasets from E-learning platforms.

I completed my Ph.D. at the University of Potsdam, where I developed methods for group formation, built a semantic database of learning goals, and created a framework for inquiry-based learning and evaluation methodologies for learning technologies. My expertise spans natural language processing, machine learning, data quality, and educational technologies.


# Experience


```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Group Lead Research Software Engineering", "GI - German Computer Science Society", "April 2025 - Present",
    "RSE, Department of Computational Social Science", c("Developing a Research Software Engineering Master Curriculum", "Research on Research Software", "Community Building and Science Policy for the new RSE field"),
    "Research Software Engineer", "GESIS - Leibniz Institute for the Social Sciences", "May 2024 - April 2025",
    "Transparent Social Analytics, Department of Computational Social Science", c("Development Lead of a project to build an Open Science platform with reusable code and tutorials", "Research on Data Quality Standards", "Implementation of tools to enhance reproducibility and facilitate research with automated quality data checks"),
    "Post Doctoral Researcher", "University of Göttingen", "Aug. 2021 - May 2024",
    "Department of Methods in Social Sciences", c("Substitute Project Coordination","Development Lead  of the Delab-Framework", "Research on Deliberation on Social Media", "Constructing Human-In-The-Loop Experiments with Reddit and Twitter, NLP with Python"),
    "Post Doctoral Researcher", "Humboldt University Berlin", "Apr. 2020 - Feb. 2021", "Chair of Learning Technologies", c("Developing new methods to detect creativity in texts", "Gathering and analyzing large datsets from E-learning Platforms"),
    "Ph.D. Candidate", "University of Potsdam", "Oct. 2014 - Oct. 2020", "Chair of Complex Computational Media Applications", c("Lead Developer of a Framework for Inquiry Based Learning", "Developing Algorithms to support Group Formation", "Construction of a Semantic Database of Learning Goals", "Developing a Methodology for the Evaluation of E-Learning", "Co-Write Project Proposals and Reports", "Active Member of the GI Junior Researcher Group")
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```
\newpage

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Ph.D. in Computer Science", "University of Potsdam", "Potsdam, Germany", "Nov. 2014 - Sep. 2020", c("Thesis: Possibilities and Limitations of Media Support for Inquiry-Based Learning", "Explores the use of computer technology to support inquiry-based learning in higher education"),
    "BA and MA in Computer Science, Political Science and Education", "University of Potsdam", "Potsdam, Germany", "Okt. 2009 - Okt. 2014", c("Thesis: An Intelligent Competence Database", "Implementation and Evaluation of a Learning Outcome Storage connected to Portfolio Learning"),
    "BA in European Studies", "University of Passau", "Passau, Germany", "April. 2007 - Sep. 2009", c("Thesis: Innenpolitische Bedingtheit europäischer Migrationspolitik", "Studying the Multilevel European System and how the Regions influenced the Amsterdam Treaty")
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```

# Languages
```{r }
#| label: language_skills
#| output: asis
tibble::tribble(
    ~category, ~languages, ~when, ~where,
    "Fluent",
    c("German: Mother tongue, fluent",
      "English: Fluent in spoken and written (TOEFL CBS 283/300)"),
    "", "Germany/Canada",
    "Advanced",
    c("French: Advanced (Certificate from the University of Geneva)",
      "Spanish: Advanced (Certificate from Maccu Picchu Spanish School)"),
    "", "Switzerland/Peru",
    "Beginner",
    c("Polish: Beginner (A1) (Unicert A1)"),
    "", "Germany",
    "Classics",
    c("Latin: Proficient (Latinum)",
      "Ancient Greek: Proficient (Graecum)"),
    "", "Germany"
) |>
    cvevents(when = "when", what = "category", where = "where", details = "languages")

```
# Shortlisted
```{r }
#| label: shortlisted_applications
#| output: asis
tibble::tribble(
    ~category, ~details, ~when, ~where,
   "Professorship", c("2nd Place TU Vienna CS Department", "4th Place Max Planck Institute for Demography (Rostock)"), "2023", "Germany/Austria",
   "Academic Councillor", c("2nd Place University of Hamburg CS Department"), "2020", "Germany"
) |>
    cvevents(when = "when", what = "category", where = "where", details = "details")

```
